Parallel Deduplication with Batch Scheduling for Collocated Virtual Machine Backup in the Cloud

### 2014-02-05 batchdedup/arch.tex
revised batchdedup paper

{\bf Snapshot deletion.} Each VM will keep a limited number of  automatically-saved snapshots and 
expired snapshots are normally deleted.
% unless its owner explicitly asks for its retention.
We adopt the idea of mark-and-sweep~\cite{Guo2011}. 
A block or a segment can be deleted if its reference count is zero.
%As we discussed in Section~\ref{sect:data}, the reference counter is kept in the global index, partitioned among machines. 
To delete useless  blocks or segments periodically, we read the meta data  of all
snapshots and compute the reference count of all blocks and segments  in parallel.
%while following the fingerprint-based partitioning.
Similar to the multi-stage duplicate detection process, reference counting is conducted in multi-stages. 
Stage  1 is to read  the segment and block  metadata 
to accumulate  reference count requests in different machines  in the fingerprint based distribution.
Stage   2 is to count references within each partition and detect those records with zero 
reference. 
%Stage 3 is that every VM gathers its z confirmed deletion requests for its content and sends them to the backup storage.
The backup  data repository logs deletion instructions,  and will periodically perform a compaction operation when 
its deletion log is too big. 
%Due to the paper constraint, we will not discuss the deletion operations in details.

>>>>

{\bf Snapshot deletion.} Each VM will keep a limited number of  automatically-saved snapshots and 
expired snapshots are normally deleted.
% unless its owner explicitly asks for its retention.
To perform compaction of unused blocks, We adopt the idea of mark-and-sweep~\cite{Guo2011}. 
A block or a segment can be deleted if its reference count is zero.
%As we discussed in Section~\ref{sect:data}, the reference counter is kept in the global index, partitioned among machines. 
To delete unreferenced blocks or segments periodically, we read the meta data  of all
snapshots and determine which blocks and segments are referenced  in parallel.
%while following the fingerprint-based partitioning.
Similar to the multi-stage duplicate detection process, marking is conducted in multiple stages. 
Stage  1 is to read  the segment and block  metadata 
to accumulate  references in different machines  based on the fingerprint based distribution.
Stage   2 is to mark blocks/segments within each partition and detect those records which are unmarked (and therefore can be deleted).
%Stage 3 is that every VM gathers its z confirmed deletion requests for its content and sends them to the backup storage.
The backup  data repository logs deletion instructions,  and will periodically perform a compaction operation when 
its deletion log is too big. 
%Due to the paper constraint, we will not discuss the deletion operations in details.

### 2014-02-05 batchdedup/eval.tex
revised batchdedup paper

%We are running our deduplication/backup  service on 100 nodes.
%Memory usage is about 150MB space per node during backup and
%the CPU usage is very small during the experiments. 
We have performed a trace-driven study using  a 1323 VM dataset  collected from 
%100 Alibaba Aliyun's cloud nodes~\cite{WeiZhangIEEE}.
a cloud cluster at Alibaba's Aliyun.
% ~\cite{WeiZhangIEEE}.
% and each of machine nodes has 16 cores and 12 disk drives,  hosting  up to 25 VMs. 
For each VM, the system keeps 10 automatically-backed snapshots in the storage while
a user may instruct extra snapshots to be saved.
The backup of VM snapshots is completed within a few  hours every night.
Based on our study of its production  data,  each VM has about  40GB of storage  data usage on average
including OS and user data disk.
Each VM image is  divided into 2 MB fix-sized segments and each segment is divided into 
variable-sized content blocks  with an average size of 4KB.
%variable sizes~\cite{similar94,rabin81} with an average size of 4KB. 
The signature for variable-sized blocks is computed using their SHA-1 hash.

>>>>

%We are running our deduplication/backup  service on 100 nodes.
%Memory usage is about 150MB space per node during backup and
%the CPU usage is very small during the experiments. 
We have performed a trace-driven study using  a 1323 VM dataset  collected from 
%100 Alibaba Aliyun's cloud nodes~\cite{WeiZhangIEEE}.
a cloud cluster at Alibaba's Aliyun. based on the data distribution from the
trace data, we have also simulated the VM size distribution of several much
larger clusters by generating synthetic traces (e.g. the two clusters in
Fig~\ref{fig:hist} have 4224 and 8046 VMs).
% ~\cite{WeiZhangIEEE}.
% and each of machine nodes has 16 cores and 12 disk drives,  hosting  up to 25 VMs. 
For each VM, the system keeps 10 automatically-backed snapshots in the storage
while a user may instruct extra snapshots to be saved.  The backup of VM
snapshots is completed within a few  hours every night.  Based on our study of
its production  data,  each VM has an average of 40GB of storage  data usage on
including OS and user data disk (though the exact size of a VM varies with a
long-tail distribution).

Each VM image is  divided into 2 MB fix-sized segments and each segment is divided into 
variable-sized content blocks  with an average size of 4KB.
%variable sizes~\cite{similar94,rabin81} with an average size of 4KB. 
The signature for variable-sized blocks is computed using their SHA-1 hash.

### 2014-02-05 batchdedup/scheduling.tex
revised batchdedup paper

\section{Multi-round Batch Scheduling}
\label{sect:scheduling}
The naive way for synchronized backup is   to schedule all of the backup tasks in one round.
Since parallel backup of these tasks goes through several stages,
that results in the backup time of each VM is approximately equal to the total execution of all backup tasks.
Given VM sizes are highly skewed in a large cluster, some big VMs will take a long time and other
small VM backup tasks synchronized in one round will have to wait.
Thus the average backup time for small VMs is fairly large.

@@

To determine how evenly distributed VM sizes are, we obtained statistical data
for 22 Aliyun clusters. The clusters in our dataset all have a very long tail
distribution, though local minima exist in the histogram and the range of VM
sizes varies. Other production clusters may have different distributions, but
all of the clusters we have looked at have similarly shaped distributions. Size
distribution histograms for two of the clusters are shown in
Fig.~\ref{fig:hist}. There is a long tail on both histrograms which has been
cut (out to 100GB for the first, and out to 2000GB for the second). The
important thing to get from this data is that in none of the productions
clusters we evaluated was the VM Size distribution flat, which motivates the
importance of round scheduling.

>>>>

\section{Multi-round Batch Scheduling}
\label{sect:scheduling}
The na\"{\i}ve way for synchronized backup is to schedule all of the backup tasks in one round.
Since parallel backup of these tasks goes through several synchronized stages,
the backup time of each VM is approximately equal to the total execution of all backup tasks.
Given VM sizes are highly skewed in a large cluster (see Fig.~\ref{fig:hist} for a plot of the distribution in several real clusters), some big VMs will take a long time and other
small VM backup tasks synchronized in one round will have to wait.
Thus the average backup time for small VMs is fairly large.

@@

To determine how evenly distributed VM sizes are, we obtained statistical data
for 22 Aliyun clusters. The clusters in our dataset all have a very long tail
distribution, though local minima exist in the histogram and the range of VM
sizes varies.
All of the clusters we have looked at have similarly shaped distributions. Size
distribution histograms for two of the clusters are shown in
Fig.~\ref{fig:hist}. There is a long tail on both histrograms which has been
cut (out to 100GB for the first, and out to 2000GB for the second). The
important thing to get from this data is that in none of the productions
clusters we evaluated was the VM Size distribution flat, which motivates the
importance of round scheduling.
